Computer Science House Constitution

### 2016-02-15 articles.tex
1 sentence = 1 line
Current diffs can be difficult to read because every paragraph inhabits
a single line. Giving each statement a line should make it easier to
track changes in the statement

\asubsection{ Non-Semantic Changes}
Any non-semantic change to the Constitution should be presented to the House for discussion. After the discussion an immediate House vote is taken.A quorum of fifty percent of the Total Number of Possible Votes must be present in order for the vote to be official. A vote exceeding fifty percent of all House members casting a vote is required for the non-semantic change to be placed into the constitution.

@@

\asubsection{Maintainer Qualifications}
Maintainers must have Active or Alumni in good standing status.

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
    \item Participate in discussion of proposals.
    \item Facilitate the creation of new changes to the Constitution by other members.
    \item Be knowledgeable about the Constitution. 
\end{itemize}
Failure to adequately meet any of these expectations is grounds for revocation of maintainer status.

\asubsection{Maintainer Resignations}
Maintainers may resign at any time by notifying the current eboard and maintainer group.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or revoked by Executive Board vote.

@@

	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated. The vacated office is then handled like any other vacated office; see \ref{Resignations}.
	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes. The members of the dual directorship need not vote the same way in a vote.

@@

	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period. Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination. Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination. A list of all nominees who have accepted their nominations will be posted shortly thereafter.

@@

	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period. The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates. In addition, an area will be provided to indicate a write-in selection of a candidate.

@@

	\item The winners are determined via the process described in \ref{Alternative Vote}. A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official. All winners are notified of their election. If the position is currently vacant, the winner immediately assumes office. If not, the winner will assume office at the end of the current term (\ref{Term}). Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.

@@

	\item The candidate is presented to the Executive Board for approval. This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained. A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.

@@

The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary. The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.

>>>>

\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented to the House for discussion followed by an Immediate Vote.
A quorum of fifty percent of the Total Number of Possible Votes is required for passage.

@@

\asubsection{Maintainer Qualifications}
Maintainers must be Active or Alumni in good standing.

\asubsection{Maintainer Expectations}
Maintainers are expected to:
\begin{itemize}
    \item Review changes to the Constitution for grammar, spelling, and internal consistency.
    \item Keep a public record of changes to the Constitution.
    \item Participate in discussion of proposals.
    \item Facilitate the creation of new changes to the Constitution by other members.
    \item Be knowledgeable about the Constitution.
\end{itemize}
Failure to meet any of these expectations is grounds for revocation of Maintainer status by the Executive Board.

\asubsection{Maintainer Resignations}
Maintainers may resign at any time by notifying the current Executive Board and Maintainer group.

\asubsection{Maintainer Term}
Maintainer status lasts until it is resigned, or until it is revoked by Executive Board vote.
If a Maintainer no longer satisfies \ref{Maintainer Qualifications}, they lose Maintainer status.

@@

	\item If one of the members in a dual directorship resigns the directorship, or for any other reason ends the term of office, the other member in the dual directorship must also step down and the office becomes vacated.
		The vacated office is then handled like any other vacated office; see \ref{Resignations}.
	\item During an official Executive Board Vote, each dual directorship member's vote counts for one-half vote in the tallying of votes.
		The members of the dual directorship need not vote the same way in a vote.

@@

	\item The opening of the Executive Board position(s) is announced at a House meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
		Any House member may nominate any eligible member or pair of members where appropriate for a Directorship.
	\item The candidates meeting the qualifications of the office they were nominated for, will be notified of their nomination.
		Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
		A list of all nominees who have accepted their nominations will be posted shortly thereafter.

@@

	\item Ballots will then be distributed and voting will be open for a minimum of a forty-eight hour period.
    The Ballots will list, in random order, all of the candidates for a given office with a means to indicate the selection of one of the candidates.
    In addition, an area will be provided to indicate a write-in selection of a candidate.

@@

	\item The winners are determined via the process described in \ref{Alternative Vote}.
    A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official.
    All winners are notified of their election.
    If the position is currently vacant, the winner immediately assumes office.
    If not, the winner will assume office at the end of the current term (\ref{Term}).
    Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Alternative Vote}.

@@

	\item The candidate is presented to the Executive Board for approval.
		This Executive Board meeting is closed to the Executive Board Members, Root Type Persons, and House members with explicit invitation from the Executive Board.
	\item All current Executive Board Voting Members must be present during the discussion and voting period unless that member is a candidate for the position, in which case the member is absent and their vote is abstained.
		A simple majority Executive Board vote, as described in \ref{Simple Majority}, is taken to determine whether the candidate is selected for the position.

@@

The Executive Board may choose to select a current voting Executive Board member, or to select any interested Active member, as House Secretary.
The selection process can be an informal appointment, or follow an election process similar to other voting Executive Board positions.
